%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer | Big Data Engineer - Trust, Identity and Safety} % Job title
    {Grab} % Organization
    {Singapore} % Location
    {May. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Architectured and implemented a streaming servicei \& pipeline that
            performs online featurization, generate transactional score and
            verdict using Apache Spark Structured Streaming (2.2), Protobuf,
            Apache Kafka, Redis and Amazon RDS.}
        \item {Designed and built a Golang micro-service for data transfer
            pipeline that ingests data from S3 into different databases (AWS RDS,
            ElasticSearch); supports various file formats, insert operations,
            multi-tenancy and databases. Replaced existing error proned bash
            scripts and delivered up to 2-5x faster transfer speed.}
        \item {Developed a syndicate and collusion ring detection using Apache
            Spark GraphX and GraphFrame}
        \item {Implemented a pipeline for syncing, parsing and wrangling logs
            for analysis (ETL with EMR and scheduled with Airflow).}
        \item {Manage and own the entire end-to-end lifecycle of designing
            models, implementation and maintenance of pipelines.}
        \item {Mentor and train junior team members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Solutions Consultant} % Job title
    {Cloudera} % Organization
    {Singapore} % Location
    {Aug. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided consultations on data architecture on Hadoop stack to
            client.}
        \item {Deployed cluster with Cloudera Hadoop Distribution - installation
            and workload tuning.}
        \item {Performed security deployment - authentication with Kerberos
            and LDAP, transport layer encryption (TLS), Role-based ACL with
            Apache Sentry.}
        \item {Performed data migration, plumbing and wrangling (with Hive and
            Impala) from existing data warehouse.}
        \item {Assisted Data Science use cases with data preparation, feature
            extractions and operationalize model (via PMML model, Scala and
            Spark).}
        \item {Worked with vendors to intergrate Kafka with TIBCO Complex Event
            Processing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead System Analyst | Senior System Analyst} % Job title
    {StarHub (Telco)} % Organization
    {Singapore} % Location
    {Feb. 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated the ETL flow consisting of data ingestion, cleaning,
            archiving and transformation into datamarts for dashboard analytics
            (via Apache Hadoop, Pig, HBase, Parquet and GreenPlum DB).}
        \item {Produced user-defined functions to ease data analysis and
            computation (Pig and GreenPlum).}
        \item {Architected and implemented services and API for higher level
            exploration of data (via Dropwizard and Elasticsearch).}
        \item {Provided mentorship and guidance to junior engineers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Savant Degrees} % Organization
    {Singapore} % Location
    {Jan. 2010 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, architected and led the building of web products
            ranging from Portfolio Management, Resources Planning System,
            Donation Platform to E-Commerce solutions}
        \item {Integrated existing systems with 3rd-party services (payment
            gateways, social media, etc.)}
        \item {Engineered and further developed in-house framework and API to
            accelerate project bootstrap and reduce development time}
        \item {Researched, championed and aligned new technologies and best
            practices into engineering team.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
